---
title: "Streamflow Duration Assessment Methods"
subtitle: "SDAM Version 1.1 Release Date: Spring 2024"
revision: "SDAM revision date: Spring, 2024" 
date: "Report generated on: `r format(Sys.time(), '%B %d, %Y')`"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
output: pdf_document
always_allow_html: no
params:
    stream_class: NA
    region: NA
    precip: NA
    drain_area: NA
    a: NA
    b: NA
    c: NA
    d: NA
    e: NA
    f: NA
    g: NA
    h: NA
    i: NA
    j: NA
    k: NA
    l: NA
    m: NA
    n: NA
    o: NA
    p: NA
    r: NA
    s: NA
    t: NA
    u: NA
    v: NA
    w: NA
    aa: NA
    ab: NA
    ac: NA
    ad: NA
    ae: NA
    af: NA
    ag: NA
    ah: NA
    ai: NA
    aj: NA
    ak: NA
    al: NA
    am: NA
    an: NA
    ao: NA
    ap: NA
    aq: NA
    ar: NA
    as: NA
    at: NA
    av: NA
    ba: NA
    bb: NA
    bc: NA
    bd: NA
    be: NA
    bf: NA
    bg: NA
    bh: NA
    bi: NA
    bl: NA
    bm: NA
    bn: NA
    bo: NA
    tbl: NA
    fff: NA
    notes_supplemental_information: NA
    f48: NA
    f48_cap: NA
    f49: NA
    f49_cap: NA
    f50: NA
    f50_cap: NA
    f51: NA
    f51_cap: NA
    aqua_inv: NA
    f6: NA
    f6_cap: NA
    f7: NA
    f7_cap: NA
    f8: NA
    f8_cap: NA
    f6_1: NA
    f6_1cap: NA
    f7_1: NA
    f7_1cap: NA
    f8_1: NA
    f8_1cap: NA
    notes_aquainv: NA
    hydro: NA
    f24: NA
    f24_cap: NA
    f25: NA
    f25_cap: NA
    f26: NA
    f26_cap: NA
    f27: NA
    f27_cap: NA
    f28: NA
    f28_cap: NA
    f29: NA
    f29_cap: NA
    notes_hydro: NA
    upland_rooted: NA
    f45: NA
    f45_cap: NA
    f46: NA
    f46_cap: NA
    f47: NA
    f47_cap: NA
    notes_rooted: NA
    algal: NA
    f36: NA
    f36_cap: NA
    f37: NA
    f37_cap: NA
    f38: NA
    f38_cap: NA
    notes_algal: NA
    vegetation: NA
    f15: NA
    f15_cap: NA
    f16: NA
    f16_cap: NA
    f17: NA
    f17_cap: NA
    notes_vegetation: NA
    slope: NA
    f21: NA
    f21_cap: NA
    f22: NA
    f22_cap: NA
    f23: NA
    f23_cap: NA
    notes_slope: NA
    riff: NA
    f42: NA
    f42_cap: NA
    f43: NA
    f43_cap: NA
    f44: NA
    f44_cap: NA
    notes_riff: NA
    bankwidth: NA
---


```{r, setup, include=FALSE}
library(knitr)
# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

# Removing all "#" from appearing in the final knit document.
knitr::opts_chunk$set(comment = NA)

# Make error messages more descriptive
options(tinytex.verbose = TRUE)

opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

<!-- *** -->

<!-- ## Classification: -->

<!-- ```{r} -->
<!-- cat(params$class_wm) -->
<!-- cat(paste0(glue::glue("Note: {params$class_wm_msg}"))) -->
<!-- ``` -->

***

## General Site Information

Project name or number: `r params$a`

Site code or identifier: `r params$c`

SDAM Region: `r params$region`

Assessor(s): `r params$b`

Waterway name: `r params$d`

Visit date: `r params$e`

Current weather conditions: `r params$bm`

Notes on current or recent weather conditions:
```{r}
cat(params$j)
```

Location: `r paste0(params$g," N, ", params$h, " E")`

Surrounding land use within 100 m: `r params$l`

Description of reach boundaries: `r params$f`

Assessment reach length (m): `r if (!is.na(params$fff)){params$fff}`

Disturbed or difficult conditions:
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
cat(params$bn)
```

Notes on disturbances or difficult site conditions:
```{r}
cat(params$k)
```

## Observed hydrology:

Percent of reach with surface flow: `r params$m`

Percent of reach with surface and sub-surface flows: `r params$n`

Number of isolated pools: `r params$o`

Notes on observed hydrology: `r params$r`

***
## Site Photos

Top of reach looking downstream:
```{r, out.width = '50%', out.height= '50%', out.extra='angle=0', fig.align='center'}
if (!identical(params[["v"]], character(0))){ 
  knitr::include_graphics(params[["v"]])
}
```

Middle of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["u"]], character(0))){ 
  knitr::include_graphics(params[["u"]])
}

```

Middle of reach looking downstream:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["t"]], character(0))){ 
  knitr::include_graphics(params[["t"]])
}
```

Bottom of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["s"]], character(0))){ 
  knitr::include_graphics(params[["s"]])
}

```

## Site Sketch

```{r, out.width='50%', fig.align='center'}
if (!identical(params[["w"]], character(0))){ 
  knitr::include_graphics(params[["w"]])
}

```

***
## Indicators


## Biological indicators


### Aquatic Invertebrates

Total abundance of aquatic benthic macroinvertebrates: `r if (!is.null(params$aqua_inv)) {params$aqua_inv}`

Notes on aquatic invertebrates:

```{r}
cat(params$notes_aquainv)
```


Aquatic invertebrate photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6"]], character(0))){ 
  knitr::include_graphics(params[["f6"]])
}
  
```


```{r}

if (!identical(params[["f6"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7"]], character(0))){ 
  knitr::include_graphics(params[["f7"]])
}
  
```

```{r}
if (!identical(params[["f7"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8"]], character(0))){ 
  knitr::include_graphics(params[["f8"]])
}

```

```{r}
if (!identical(params[["f8"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_cap, perl = TRUE)))
}
```



```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6_1"]], character(0))){ 
  knitr::include_graphics(params[["f6_1"]])
}
  
```


```{r}

if (!identical(params[["f6_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_1cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7_1"]], character(0))){ 
  knitr::include_graphics(params[["f7_1"]])
}
  
```

```{r}
if (!identical(params[["f7_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_1cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8_1"]], character(0))){ 
  knitr::include_graphics(params[["f8_1"]])
}

```

```{r}
if (!identical(params[["f8_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_1cap, perl = TRUE)))
}
```



### Hydrophytes
Number of hydrophytic plant species: `r if (!is.null(params$hydro)) {params$hydro}`

Notes on hydrophytic plants:

```{r}
cat(params$notes_hydro)
```


Hydrophyte photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f24"]], character(0))){ 
  knitr::include_graphics(params[["f24"]])
}
  
```


```{r}

if (!identical(params[["f24"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f24_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f25"]], character(0))){ 
  knitr::include_graphics(params[["f25"]])
}
  
```

```{r}
if (!identical(params[["f25"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f25_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f26"]], character(0))){ 
  knitr::include_graphics(params[["f26"]])
}

```

```{r}
if (!identical(params[["f26"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f26_cap, perl = TRUE)))
}
```



```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f27"]], character(0))){ 
  knitr::include_graphics(params[["f27"]])
}
  
```


```{r}

if (!identical(params[["f27"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f27_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f28"]], character(0))){ 
  knitr::include_graphics(params[["f28"]])
}
  
```

```{r}
if (!identical(params[["f28"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f28_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f29"]], character(0))){ 
  knitr::include_graphics(params[["f29"]])
}

```

```{r}
if (!identical(params[["f29"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f29_cap, perl = TRUE)))
}
```


### Algal Cover

Algal cover Score: `r if (!is.null(params$algal)){params$algal}`

Notes about algal cover:

```{r}
cat(params$notes_algal)
```

Algal cover photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f36"]], character(0))){ 
    knitr::include_graphics(params[["f36"]])
}

```

```{r}
if (!identical(params[["f36"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f36_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f37"]], character(0))){ 
    knitr::include_graphics(params[["f37"]])
}

```

```{r}
if (!identical(params[["f37"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f37_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f38"]], character(0))){ 
    knitr::include_graphics(params[["f38"]])
} 

```

```{r}
if (!identical(params[["f38"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f38_cap, perl = TRUE)))
}
```


***
## Geomorphic Indicators

### Upland Rooted Plants

Upland Rooted Plants score: `r if (!is.null(params$upland_rooted)){params$upland_rooted}`


Notes about absence of upland rooted plants in streambed:

```{r}
cat(params$notes_rooted)
```


Upland Rooted Plants photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f45"]], character(0))){ 
  knitr::include_graphics(params[["f45"]])
}

```

```{r}
if (!identical(params[["f45"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f45_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f46"]], character(0))){ 
  knitr::include_graphics(params[["f46"]])
} 

```

```{r}
if (!identical(params[["f46"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f46_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f47"]], character(0))){ 
  knitr::include_graphics(params[["f47"]])
}

```

```{r}
if (!identical(params[["f47"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f47_cap, perl = TRUE)))
}
```


### Differences in Vegetation

Differences in vegetation score: `r if (!is.null(params$veg)){params$veg}`


Notes about differences in vegetation:

```{r}
cat(params$notes_vegetation)
```


Vegetation photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f15"]], character(0))){ 
  knitr::include_graphics(params[["f15"]])
}

```

```{r}
if (!identical(params[["f15"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f15_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f16"]], character(0))){ 
  knitr::include_graphics(params[["f16"]])
} 

```

```{r}
if (!identical(params[["f16"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f16_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f17"]], character(0))){ 
  knitr::include_graphics(params[["f17"]])
}

```

```{r}
if (!identical(params[["f17"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f17_cap, perl = TRUE)))
}
```


### Riffle Pool Sequence Score

Riffle pool sequence score: `r if (!is.null(params$riff)){params$riff}`


Notes about riffle pool sequence:

```{r}
cat(params$notes_riff)
```


Riffle and pool photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f42"]], character(0))){ 
  knitr::include_graphics(params[["f42"]])
}

```

```{r}
if (!identical(params[["f42"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f42_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f43"]], character(0))){ 
  knitr::include_graphics(params[["f43"]])
} 

```

```{r}
if (!identical(params[["f43"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f43_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f44"]], character(0))){ 
  knitr::include_graphics(params[["f44"]])
}

```

```{r}
if (!identical(params[["f44"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f44_cap, perl = TRUE)))
}
```




***

### Bankfull channel width (m): `r params$bankwidth`

***

### Slope

Slope Percent: `r if (!is.null(params$slope)){params$slope}`

<!-- 2x maximum bankfull depth (m.m): `r if (!is.null(params$bank2x)){params$bank2x}` -->

<!-- Flood-prone width (m.m): `r if (!is.null(params$fpw)){params$fpw}` -->

<!-- Entrenchment Ratio: `r if (!is.null(params$entrenchment)){params$entrenchment}` -->

Notes about slope:

```{r}
cat(params$notes_slope)
```


Slope photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f21"]], character(0))){ 
    knitr::include_graphics(params[["f21"]])
}

```

```{r}
if (!identical(params[["f21"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f21_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f22"]], character(0))){ 
    knitr::include_graphics(params[["f22"]])
}
```

```{r}
if (!identical(params[["f22"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f22_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f23"]], character(0))){ 
    knitr::include_graphics(params[["f23"]])
}

```

```{r}
if (!identical(params[["f23"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f23_cap, perl = TRUE)))
}
```

***

## Supplemental Information

Additional notes about the assessment:

```{r}
cat(params$notes_supplemental_information)
```

Supplemental information photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f48"]], character(0))){ 
    knitr::include_graphics(params[["f48"]])
}

```

```{r}
if (!identical(params[["f48"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f48_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f49"]], character(0))){ 
    knitr::include_graphics(params[["f49"]])
}
```

```{r}
if (!identical(params[["f49"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f49_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f50"]], character(0))){ 
    knitr::include_graphics(params[["f50"]])
}

```

```{r}
if (!identical(params[["f50"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f50_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f51"]], character(0))){ 
    knitr::include_graphics(params[["f51"]])
}

```

```{r}
if (!identical(params[["f51"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f51_cap, perl = TRUE)))
}
```



*** 

## `r params$stream_class`

***



**End of Report**

