---
title: "Streamflow Duration Assessment Methods"
subtitle: "SDAM Version 1.1 Release Date: Spring 2024"
revision: "SDAM revision date: Spring, 2024" 
date: "Report generated on: `r format(Sys.time(), '%B %d, %Y')`"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
output: pdf_document
always_allow_html: no
params:
   stream_class: NA
    region: NA
    precip: NA
    drain_area: NA
    a: NA
    b: NA
    c: NA
    d: NA
    e: NA
    bm: NA
    j: NA
    g: NA
    h: NA
    l: NA
    fff: NA
    bn: NA
    v: NA
    u: NA
    t: NA
    s: NA
    m: NA
    n: NA
    o: NA
    r: NA
    w: NA
    notes_supplemental_information: NA
    f48: NA
    f48_cap: NA
    f49: NA
    f49_cap: NA
    f50: NA
    f50_cap: NA
    f51: NA
    f51_cap: NA
    aqua_inv: NA
    ephem: NA
    f6: NA
    f6_cap: NA
    f7: NA
    f7_cap: NA
    f8: NA
    f8_cap: NA
    f6_1: NA
    f6_1cap: NA
    f7_1: NA
    f7_1cap: NA
    f8_1: NA
    f8_cap: NA
    notes_aquainv: NA
    hydro: NA
    f24: NA
    f24_cap: NA
    f25: NA
    f25_cap: NA
    f26: NA
    f26_cap: NA
    f27: NA
    f27_cap: NA
    f28: NA
    f28_cap: NA
    f29: NA
    f29_cap: NA
    notes_hydro: NA
    per_taxa: NA
    f33: NA
    f33_cap: NA
    f34: NA
    f34_cap: NA
    f35: NA
    f35_cap: NA
    notes_per: NA
    fish: NA
    f30: NA
    f30_cap: NA
    f31: NA
    f31_cap: NA
    f32: NA
    f32_cap: NA
    notes_fish: NA
    amphibians: NA
    f39: NA
    f39_cap: NA
    f40: NA
    f40_cap: NA
    f41: NA
    f41_cap: NA
    notes_amph: NA
    slope: NA
    f21: NA
    f21_cap: NA
    f22: NA
    f22_cap: NA
    f23: NA
    f23_cap: NA
    notes_slope: NA
  
---


```{r, setup, include=FALSE}
library(knitr)
# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

# Removing all "#" from appearing in the final knit document.
knitr::opts_chunk$set(comment = NA)

# Make error messages more descriptive
options(tinytex.verbose = TRUE)

opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

<!-- *** -->

<!-- ## Classification: -->

<!-- ```{r} -->
<!-- cat(params$class_wm) -->
<!-- cat(paste0(glue::glue("Note: {params$class_wm_msg}"))) -->
<!-- ``` -->

***

## General Site Information

Project name or number: `r params$a`

Site code or identifier: `r params$c`

SDAM Region: `r params$region`

Assessor(s): `r params$b`

Waterway name: `r params$d`

Visit date: `r params$e`

Current weather conditions: `r params$bm`

Notes on current or recent weather conditions:
```{r}
cat(params$j)
```

Location: `r paste0(params$g," N, ", params$h, " E")`

Surrounding land use within 100 m: `r params$l`

Description of reach boundaries: `r params$f`

Assessment reach length (m): `r if (!is.na(params$fff)){params$fff}`

Disturbed or difficult conditions:
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
cat(params$bn)
```

Notes on disturbances or difficult site conditions:
```{r}
cat(params$k)
```

## Observed hydrology:

Percent of reach with surface flow: `r params$m`

Percent of reach with surface and sub-surface flows: `r params$n`

Number of isolated pools: `r params$o`

Notes on observed hydrology: `r params$r`

***
## Site Photos

Top of reach looking downstream:
```{r, out.width = '50%', out.height= '50%', out.extra='angle=0', fig.align='center'}
if (!identical(params[["v"]], character(0))){ 
  knitr::include_graphics(params[["v"]])
}
```

Middle of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["u"]], character(0))){ 
  knitr::include_graphics(params[["u"]])
}

```

Middle of reach looking downstream:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["t"]], character(0))){ 
  knitr::include_graphics(params[["t"]])
}
```

Bottom of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["s"]], character(0))){ 
  knitr::include_graphics(params[["s"]])
}

```

## Site Sketch

```{r, out.width='50%', fig.align='center'}
if (!identical(params[["w"]], character(0))){ 
  knitr::include_graphics(params[["w"]])
}

```

***
## Indicators


## Biological indicators


### Aquatic Invertebrates

Aquatic benthic macroinvertebrates present: `r if (!is.null(params$aqua_inv)) {params$aqua_inv}`
Six or more individuals of the order of Ephemeroptera present: `r if (!is.null(params$ephem)) {params$ephem}`

Notes on aquatic invertebrates:

```{r}
cat(params$notes_aquainv)
```


Aquatic invertebrate photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6"]], character(0))){ 
  knitr::include_graphics(params[["f6"]])
}
  
```


```{r}

if (!identical(params[["f6"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7"]], character(0))){ 
  knitr::include_graphics(params[["f7"]])
}
  
```

```{r}
if (!identical(params[["f7"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8"]], character(0))){ 
  knitr::include_graphics(params[["f8"]])
}

```

```{r}
if (!identical(params[["f8"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_cap, perl = TRUE)))
}
```



```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6_1"]], character(0))){ 
  knitr::include_graphics(params[["f6_1"]])
}
  
```


```{r}

if (!identical(params[["f6_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_1cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7_1"]], character(0))){ 
  knitr::include_graphics(params[["f7_1"]])
}
  
```

```{r}
if (!identical(params[["f7_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_1cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8_1"]], character(0))){ 
  knitr::include_graphics(params[["f8_1"]])
}

```

```{r}
if (!identical(params[["f8_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_1cap, perl = TRUE)))
}
```



### Hydrophytes
FACW, OBL, or SAV plants present (within ½ channel width): `r if (!is.null(params$hydro)) {params$hydro}`

Notes on hydrophytic plants:

```{r}
cat(params$notes_hydro)
```


Hydrophyte photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f24"]], character(0))){ 
  knitr::include_graphics(params[["f24"]])
}
  
```


```{r}

if (!identical(params[["f24"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f24_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f25"]], character(0))){ 
  knitr::include_graphics(params[["f25"]])
}
  
```

```{r}
if (!identical(params[["f25"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f25_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f26"]], character(0))){ 
  knitr::include_graphics(params[["f26"]])
}

```

```{r}
if (!identical(params[["f26"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f26_cap, perl = TRUE)))
}
```



```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f27"]], character(0))){ 
  knitr::include_graphics(params[["f27"]])
}
  
```


```{r}

if (!identical(params[["f27"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f27_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f28"]], character(0))){ 
  knitr::include_graphics(params[["f28"]])
}
  
```

```{r}
if (!identical(params[["f28"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f28_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f29"]], character(0))){ 
  knitr::include_graphics(params[["f29"]])
}

```

```{r}
if (!identical(params[["f29"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f29_cap, perl = TRUE)))
}
```


### Fish

Fish present: `r if (!is.null(params$fish)){params$fish}`

Notes about fish:

```{r}
cat(params$notes_fish)
```

Fish photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f30"]], character(0))){ 
    knitr::include_graphics(params[["f30"]])
}

```

```{r}
if (!identical(params[["f30"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f30_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f31"]], character(0))){ 
    knitr::include_graphics(params[["f31"]])
}

```

```{r}
if (!identical(params[["f31"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f31_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f32"]], character(0))){ 
    knitr::include_graphics(params[["f32"]])
} 

```

```{r}
if (!identical(params[["f32"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f32_cap, perl = TRUE)))
}
```


### Amphibians

Amphibians present: `r if (!is.null(params$amphibians)){params$amphibians}`


Notes about amphibians:

```{r}
cat(params$notes_amph)
```


Amphbian photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f39"]], character(0))){ 
  knitr::include_graphics(params[["f39"]])
}

```

```{r}
if (!identical(params[["f39"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f39_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f40"]], character(0))){ 
  knitr::include_graphics(params[["f40"]])
} 

```

```{r}
if (!identical(params[["f40"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f40_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f41"]], character(0))){ 
  knitr::include_graphics(params[["f41"]])
}

```

```{r}
if (!identical(params[["f41"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f41_cap, perl = TRUE)))
}
```


### Perennial Taxa

Perennial taxa present: `r if (!is.null(params$per_taxa)){params$per_taxa}`


Notes about perennial taxa:

```{r}
cat(params$notes_per)
```


Perennial taxa photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f33"]], character(0))){ 
  knitr::include_graphics(params[["f33"]])
}

```

```{r}
if (!identical(params[["f33"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f33_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f34"]], character(0))){ 
  knitr::include_graphics(params[["f34"]])
} 

```

```{r}
if (!identical(params[["f34"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f34_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f35"]], character(0))){ 
  knitr::include_graphics(params[["f35"]])
}

```

```{r}
if (!identical(params[["f35"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f35_cap, perl = TRUE)))
}
```

***

### Slope

Slope Percent: `r if (!is.null(params$slope)){params$slope}`

<!-- 2x maximum bankfull depth (m.m): `r if (!is.null(params$bank2x)){params$bank2x}` -->

<!-- Flood-prone width (m.m): `r if (!is.null(params$fpw)){params$fpw}` -->

<!-- Entrenchment Ratio: `r if (!is.null(params$entrenchment)){params$entrenchment}` -->

Notes about slope:

```{r}
cat(params$notes_slope)
```


Slope photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f21"]], character(0))){ 
    knitr::include_graphics(params[["f21"]])
}

```

```{r}
if (!identical(params[["f21"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f21_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f22"]], character(0))){ 
    knitr::include_graphics(params[["f22"]])
}
```

```{r}
if (!identical(params[["f22"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f22_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f23"]], character(0))){ 
    knitr::include_graphics(params[["f23"]])
}

```

```{r}
if (!identical(params[["f23"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f23_cap, perl = TRUE)))
}
```

***

## Supplemental Information

Additional notes about the assessment:

```{r}
cat(params$notes_supplemental_information)
```

Supplemental information photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f48"]], character(0))){ 
    knitr::include_graphics(params[["f48"]])
}

```

```{r}
if (!identical(params[["f48"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f48_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f49"]], character(0))){ 
    knitr::include_graphics(params[["f49"]])
}
```

```{r}
if (!identical(params[["f49"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f49_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f50"]], character(0))){ 
    knitr::include_graphics(params[["f50"]])
}

```

```{r}
if (!identical(params[["f50"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f50_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f51"]], character(0))){ 
    knitr::include_graphics(params[["f51"]])
}

```

```{r}
if (!identical(params[["f51"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f51_cap, perl = TRUE)))
}
```



*** 

## `r params$stream_class`

***



**End of Report**

