---
title: \vspace{-2cm} \begin{Huge} Streamflow Duration Assessment Methods \end{Huge}
subtitle: "SDAM Version 1.1 Release Date: Spring 2024"
revision: "SDAM revision date: Spring, 2024" 
date: "Report generated on: `r format(Sys.time(), '%B %d, %Y')`"
header-includes:
- \usepackage{xcolor}
- \usepackage{fancyhdr}
- \renewcommand{\headrulewidth}{0.0pt}
- \pagestyle{fancy}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
output: pdf_document
always_allow_html: no
params:
    stream_class: NA
    region: NA
    precip: NA
    drain_area: NA
    adj_regions: NA
    a: NA
    b: NA
    c: NA
    d: NA
    e: NA
    f: NA
    g: NA
    h: NA
    i: NA
    j: NA
    k: NA
    l: NA
    m: NA
    n: NA
    o: NA
    p: NA
    r: NA
    s: NA
    t: NA
    u: NA
    v: NA
    w: NA
    aa: NA
    ab: NA
    ac: NA
    ad: NA
    ae: NA
    af: NA
    ag: NA
    ah: NA
    ai: NA
    aj: NA
    ak: NA
    al: NA
    am: NA
    an: NA
    ao: NA
    ap: NA
    aq: NA
    ar: NA
    as: NA
    at: NA
    av: NA
    ba: NA
    bb: NA
    bc: NA
    bd: NA
    be: NA
    bf: NA
    bg: NA
    bh: NA
    bi: NA
    bl: NA
    bm: NA
    bn: NA
    bo: NA
    tbl: NA
    fff: NA
    notes_supplemental_information: NA
    f48: NA
    f48_cap: NA
    f49: NA
    f49_cap: NA
    f50: NA
    f50_cap: NA
    f51: NA
    f51_cap: NA
    aqua_inv: NA
    ephem: NA
    f6: NA
    f6_cap: NA
    f7: NA
    f7_cap: NA
    f8: NA
    f8_cap: NA
    f6_1: NA
    f6_1cap: NA
    f7_1: NA
    f7_1cap: NA
    f8_1: NA
    f8_1cap: NA
    notes_aquainv: NA
    hydro: NA
    f24: NA
    f24_cap: NA
    f25: NA
    f25_cap: NA
    f26: NA
    f26_cap: NA
    f27: NA
    f27_cap: NA
    f28: NA
    f28_cap: NA
    f29: NA
    f29_cap: NA
    notes_hydro: NA
    per_taxa: NA
    f33: NA
    f33_cap: NA
    f34: NA
    f34_cap: NA
    f35: NA
    f35_cap: NA
    notes_per: NA
    fish: NA
    f30: NA
    f30_cap: NA
    f31: NA
    f31_cap: NA
    f32: NA
    f32_cap: NA
    notes_fish: NA
    amphibians: NA
    f39: NA
    f39_cap: NA
    f40: NA
    f40_cap: NA
    f41: NA
    f41_cap: NA
    notes_amph: NA
    slope: NA
    f21: NA
    f21_cap: NA
    f22: NA
    f22_cap: NA
    f23: NA
    f23_cap: NA
    notes_slope: NA
    hp1: NA
    hp2: NA
    hp3: NA
    notes_landuse: NA
  
---


```{r, setup, include=FALSE}
library(knitr)
library(ggplot2)
library(usmap)
# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

# Removing all "#" from appearing in the final knit document.
knitr::opts_chunk$set(comment = NA)

# Make error messages more descriptive
options(tinytex.verbose = TRUE)

opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

```{r, out.width='32%', fig.align='center', fig.show='hold'}

knitr::include_graphics(c(params$hp1, params$hp2, params$hp3))

```

```{r, out.width='100%', out.height='50%'}
if (params$h != 'Not Provided'){
  x <- data.frame(lon = params$h, lat = params$g, type = 'Site Location')

  transformed_data <- usmap_transform(x)

  plot_usmap("states") + 
          geom_point(data = transformed_data, 
                    aes(x = transformed_data$geometry[1][[1]][1], 
                        y = transformed_data$geometry[1][[1]][2],
                        fill = type
                        ), 
                    color = "red",
                    size = 5)  + 
          theme(legend.position = 'bottom',
                legend.direction = 'horizontal',
                legend.title = element_blank(),
                legend.text=element_text(size=12))
}
```

\pagebreak


\begin{center}
\textbf{\underline{\LARGE{General Site Information}}}
\end{center}

Project name or number: `r params$a`

Site code or identifier: `r params$c`

SDAM Region: `r params$region`

Adjacent SDAM Regions within 10 Miles: `r params$adj_regions`

Assessor(s): `r params$b`

Waterway name: `r params$d`

Visit date: `r params$e`

Current weather conditions: `r params$bm`

Notes on current or recent weather conditions:
```{r}
cat(params$j)
```

Location: `r paste0(params$g," N, ", params$h, " E")`

Surrounding land use within 100 m: `r params$l`

Notes on land use: `r params$notes_landuse`

Description of reach boundaries: `r params$f`

Assessment reach length (m): `r if (!is.na(params$fff)){params$fff}`

Disturbed or difficult conditions:
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
cat(params$bn)
```

Notes on disturbances or difficult site conditions:
```{r}
cat(params$k)
```

\vspace{3mm}
\begin{center}
\textbf{\underline{\LARGE{Observed Hydrology}}}
\end{center}

Percent of reach with surface flow: `r params$m`

Percent of reach with surface and sub-surface flows: `r params$n`

Number of isolated pools: `r params$o`

Notes on observed hydrology: `r params$r`

\vspace{3mm}
\begin{center}
\textbf{\underline{\LARGE{Site Photos}}}
\end{center}

Top of reach looking downstream:
```{r, out.width = '50%', out.height= '50%', out.extra='angle=0', fig.align='center'}
if (!identical(params[["v"]], character(0))){ 
  knitr::include_graphics(params[["v"]])
}
```

Middle of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["u"]], character(0))){ 
  knitr::include_graphics(params[["u"]])
}

```

Middle of reach looking downstream:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["t"]], character(0))){ 
  knitr::include_graphics(params[["t"]])
}
```

Bottom of reach looking upstream:
```{r, out.width='50%', fig.align='center'}
if (!identical(params[["s"]], character(0))){ 
  knitr::include_graphics(params[["s"]])
}

```

\vspace{3mm}
\begin{center}
\textbf{\underline{\LARGE{Site Sketch}}}
\end{center}


```{r, out.width='50%', fig.align='center'}
if (!identical(params[["w"]], character(0))){ 
  knitr::include_graphics(params[["w"]])
}

```

\vfill
\noindent\rule{16cm}{2pt}\
\pagebreak

\begin{center}
\textbf{\underline{\LARGE{Biological Indicators}}}
\end{center}


\vspace{2mm}
\textbf{\large{Aquatic Invertebrates}}

Aquatic benthic macroinvertebrates present: `r if (!is.null(params$aqua_inv)) {params$aqua_inv}`
 
Six or more individuals of the order of Ephemeroptera present: `r if (!is.null(params$ephem)) {params$ephem}`

Notes on aquatic invertebrates:

```{r}
cat(params$notes_aquainv)
```


Aquatic invertebrate photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6"]], character(0))){ 
  knitr::include_graphics(params[["f6"]])
}
  
```


```{r}

if (!identical(params[["f6"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7"]], character(0))){ 
  knitr::include_graphics(params[["f7"]])
}
  
```

```{r}
if (!identical(params[["f7"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8"]], character(0))){ 
  knitr::include_graphics(params[["f8"]])
}

```

```{r}
if (!identical(params[["f8"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_cap, perl = TRUE)))
}
```



```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f6_1"]], character(0))){ 
  knitr::include_graphics(params[["f6_1"]])
}
  
```


```{r}

if (!identical(params[["f6_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f6_1cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f7_1"]], character(0))){ 
  knitr::include_graphics(params[["f7_1"]])
}
  
```

```{r}
if (!identical(params[["f7_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f7_1cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f8_1"]], character(0))){ 
  knitr::include_graphics(params[["f8_1"]])
}

```

```{r}
if (!identical(params[["f8_1"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f8_1cap, perl = TRUE)))
}
```



\vspace{2mm}
\textbf{\large{Hydrophytes}}

Number of hydrophytic plant species: `r if (!is.null(params$hydro)) {params$hydro}`

FACW, OBL, or SAV plants present (within ½ channel width): `r if (!is.null(params$hydro)) {params$hydro}`

Notes on hydrophytic plants:

```{r}
cat(params$notes_hydro)
```


Hydrophyte photos and photo descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f24"]], character(0))){ 
  knitr::include_graphics(params[["f24"]])
}
  
```


```{r}

if (!identical(params[["f24"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f24_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f25"]], character(0))){ 
  knitr::include_graphics(params[["f25"]])
}
  
```

```{r}
if (!identical(params[["f25"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f25_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f26"]], character(0))){ 
  knitr::include_graphics(params[["f26"]])
}

```

```{r}
if (!identical(params[["f26"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f26_cap, perl = TRUE)))
}
```



```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f27"]], character(0))){ 
  knitr::include_graphics(params[["f27"]])
}
  
```


```{r}

if (!identical(params[["f27"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f27_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f28"]], character(0))){ 
  knitr::include_graphics(params[["f28"]])
}
  
```

```{r}
if (!identical(params[["f28"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f28_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f29"]], character(0))){ 
  knitr::include_graphics(params[["f29"]])
}

```

```{r}
if (!identical(params[["f29"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f29_cap, perl = TRUE)))
}
```


\vspace{2mm}
\textbf{\large{Fish}}

Fish present: `r if (!is.null(params$fish)){params$fish}`

Notes about fish:

```{r}
cat(params$notes_fish)
```

Fish photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f30"]], character(0))){ 
    knitr::include_graphics(params[["f30"]])
}

```

```{r}
if (!identical(params[["f30"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f30_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f31"]], character(0))){ 
    knitr::include_graphics(params[["f31"]])
}

```

```{r}
if (!identical(params[["f31"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f31_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f32"]], character(0))){ 
    knitr::include_graphics(params[["f32"]])
} 

```

```{r}
if (!identical(params[["f32"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f32_cap, perl = TRUE)))
}
```

\vspace{2mm}
\textbf{\large{Amphibians}}

Amphibians present: `r if (!is.null(params$amphibians)){params$amphibians}`


Notes about amphibians:

```{r}
cat(params$notes_amph)
```


Amphbian photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f39"]], character(0))){ 
  knitr::include_graphics(params[["f39"]])
}

```

```{r}
if (!identical(params[["f39"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f39_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f40"]], character(0))){ 
  knitr::include_graphics(params[["f40"]])
} 

```

```{r}
if (!identical(params[["f40"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f40_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f41"]], character(0))){ 
  knitr::include_graphics(params[["f41"]])
}

```

```{r}
if (!identical(params[["f41"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f41_cap, perl = TRUE)))
}
```

\vspace{2mm}
\textbf{\large{Perennial Taxa}}

Perennial taxa present: `r if (!is.null(params$per_taxa)){params$per_taxa}`


Notes about perennial taxa:

```{r}
cat(params$notes_per)
```


Perennial taxa photos and descriptions:

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f33"]], character(0))){ 
  knitr::include_graphics(params[["f33"]])
}

```

```{r}
if (!identical(params[["f33"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f33_cap, perl = TRUE)))
}
```


```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f34"]], character(0))){ 
  knitr::include_graphics(params[["f34"]])
} 

```

```{r}
if (!identical(params[["f34"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f34_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f35"]], character(0))){ 
  knitr::include_graphics(params[["f35"]])
}

```

```{r}
if (!identical(params[["f35"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f35_cap, perl = TRUE)))
}
```

\vspace{2mm}
\textbf{\large{Slope}}

Slope Percent: `r if (!is.null(params$slope)){params$slope}`

<!-- 2x maximum bankfull depth (m.m): `r if (!is.null(params$bank2x)){params$bank2x}` -->

<!-- Flood-prone width (m.m): `r if (!is.null(params$fpw)){params$fpw}` -->

<!-- Entrenchment Ratio: `r if (!is.null(params$entrenchment)){params$entrenchment}` -->

Notes about slope:

```{r}
cat(params$notes_slope)
```


Slope photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f21"]], character(0))){ 
    knitr::include_graphics(params[["f21"]])
}

```

```{r}
if (!identical(params[["f21"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f21_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f22"]], character(0))){ 
    knitr::include_graphics(params[["f22"]])
}
```

```{r}
if (!identical(params[["f22"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f22_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f23"]], character(0))){ 
    knitr::include_graphics(params[["f23"]])
}

```

```{r}
if (!identical(params[["f23"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f23_cap, perl = TRUE)))
}
```

\vfill
\noindent\rule{16cm}{2pt}\
\pagebreak

\begin{center}
\textbf{\underline{\LARGE{Supplemental Information}}}
\end{center}

Additional notes about the assessment:

```{r}
cat(params$notes_supplemental_information)
```

Supplemental information photos and descriptions:
```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f48"]], character(0))){ 
    knitr::include_graphics(params[["f48"]])
}

```

```{r}
if (!identical(params[["f48"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f48_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f49"]], character(0))){ 
    knitr::include_graphics(params[["f49"]])
}
```

```{r}
if (!identical(params[["f49"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f49_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f50"]], character(0))){ 
    knitr::include_graphics(params[["f50"]])
}

```

```{r}
if (!identical(params[["f50"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f50_cap, perl = TRUE)))
}
```

```{r, out.width='50%', fig.align='center'}

if (!identical(params[["f51"]], character(0))){ 
    knitr::include_graphics(params[["f51"]])
}

```

```{r}
if (!identical(params[["f51"]], character(0))){ 
  cat(paste0("Description: ",gsub('(?=(?:.{91})+$)', "\n", params$f51_cap, perl = TRUE)))
}
```


\noindent\rule{16cm}{2.5pt}\
\textbf{\Large{`r params$stream_class`}}

\noindent\rule{16cm}{2.5pt}

\begin{center}
\textbf{\underline{\LARGE{Additional Resources}}}
\end{center}


[\textcolor{cyan}{User Manual}](https://www.epa.gov/streamflow-duration-assessment)

[\textcolor{cyan}{Field Form}](https://www.epa.gov/streamflow-duration-assessment)

[\textcolor{cyan}{Training Materials}](https://www.epa.gov/streamflow-duration-assessment)

[\textcolor{cyan}{SDAMs Home}](https://www.epa.gov/streamflow-duration-assessment)
 
\vfill
\noindent\rule{16cm}{3pt}\
\begin{center}
\textbf{\LARGE{End of Report}}
\end{center}
